A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-16 paper/theor-experiment.tex
clean up

\subsubsection{Hyper parameter Scan}
While the optimization problem and goals were well defined (Subsection \ref{awaproblem}), 
it was not clear what the best hyper parameters for the genetic algorithm would be.
These parameters include gene mutation probability, mutation probability, 
recombination probability, number of individuals, 
and number of generations to complete. 
Given the beam line in Fig.~\ref{awa-linac},
four small optimization experiments were done with various NSGA-II parameters. 
Similar to the time step scan, 
the goal of this exercise was to determine which set of optimization
parameters strongly influence the results, 
and whether there was a time to solution difference.
From here on, we will reference each experiment as ex-1, ex-2, ex-3, and ex-4
as shown in Table \ref{extable}. 
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. 
			The max number of individuals per generation was~80.}
		\label{extable}
		\begin{tabular*}{0.48\textwidth}{l @{\extracolsep{\fill}} C C D }
			\hline\noalign{\smallskip}
			& Gene Mutation Probability & Recombination Probibility & Number of completed generations \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			ex-1 &  0.1  & 0.9  &  96 \\
			ex-2 &  0.3  & 0.7  &  81 \\
			ex-3 &  0.8  & 0.2  &  53 \\
			ex-4 &  0.01 & 0.09 &  95 \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}
	\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
	\label{fig:pareto1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
	\llap{\raisebox{1.9cm}{%  move next graphics to top right corner
			\includegraphics[height=4.5cm]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5}%
	}}
	\caption{Pareto front comparing energy spread (dE) and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
	\label{fig:pareto2}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xyrms-zrms_newobj}\\
	\vspace{2em}
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}
	\caption{Optimized beam sizes along high charge beam line.}
	\label{fig:stat}
\end{figure}

>>>>

\subsubsection{Hyper parameter Scan}
While the optimization problem and goals were well defined (Subsection \ref{awaproblem}), 
it was not clear what the best hyper parameters for the genetic algorithm would be.
These parameters include gene mutation probability, mutation probability, 
recombination probability, number of individuals, 
and number of generations to complete. 
Given the beam line in Fig.~\ref{awa-linac},
four small optimization experiments were done with various NSGA-II parameters. 
Similar to the time step scan, 
the goal of this exercise was to determine which set of optimization
parameters strongly influence the results, 
and whether there was a time to solution difference.
From here on, we will reference each experiment as ex-1, ex-2, ex-3, and ex-4
as shown in Table \ref{extable}. 
\begin{table}%[h!]
	\begin{center}
		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. 
			The max number of individuals per generation was~80.}
		\label{extable}
		\begin{tabular*}{0.48\textwidth}{l @{\extracolsep{\fill}} C C D }
			\hline\noalign{\smallskip}
			& Gene Mutation Probability & Recombination Probability & Number of completed generations \\
			\noalign{\smallskip}\hline\noalign{\smallskip}
			ex-1 &  0.1  & 0.9  &  96 \\
			ex-2 &  0.3  & 0.7  &  81 \\
			ex-3 &  0.8  & 0.2  &  53 \\
			ex-4 &  0.01 & 0.09 &  95 \\
			\noalign{\smallskip}\hline
		\end{tabular*}
	\end{center}
\end{table}

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/safehold/xy_vs_pxy_pareto_front_quads_before_Q5}
	\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
	\label{fig:pareto1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/safehold/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
	\llap{\raisebox{1.9cm}{%  move next graphics to top right corner
			\includegraphics[height=4.5cm]{../pareto_stat_plots/safehold/dE_vs_zrms_pareto_front_quads_before_Q5}%
	}}
	\caption{Pareto front comparing energy spread (dE) and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
	\label{fig:pareto2}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/safehold/xy-max-min-zrms_newobj}
	\caption{Optimized beam sizes along high charge beam line.}
	\label{fig:stat}
\end{figure}
